开题报告

### 2019-07-22 report/06-aqi-gamm.Rmd
fixup

library(gamsel)
gam1 <- gamsel(as.matrix(dat.sel.y[,-c(1:3, 23:24)]), as.matrix(dat.sel.y[,3]))
## summary(gam1)

@@

library(gamsel)
gam1 <- gamsel(as.matrix(dat.sel.m[,-c(1:4, 24:25)]), as.matrix(log(dat.sel.m[,4])))
## summary(gam1)

par(mfrow=c(6,4), mar=c(2.1, 3.1, 2.1, 1.1))
## plot(gam1,newx=as.matrix(dat.sel.m[,-c(1, 23:24)]), index=22)
mapply(function(i, y) {
    plot(gam1,newx=as.matrix(dat.sel.m[,-c(1:4, 24:25)]),
         index=22, which = i, main = y, cex.main = 0.95, ylim = c(-0.2, 0.2))},
    as.list(1:22),
    as.list(varinfo[,2][-c(1:4, 24:25)]))

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "coast", "heating", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "coast", "heating", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
lme.y <- gamm(AQI~invest+car+gas_control+mean_temp+rain+humid+wind_speed+pressure+coast+heating+lat,
              random=list(city=~1), data=dat.sel.y, method = "REML")

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "coast", "heating", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
gam.y <- gam(AQI~te(invest)+te(car)+gas_control+te(mean_temp)+rain+humid+wind_speed+pressure+coast+heating+lat,
             data=dat.sel.y, method = "REML")

@@

```{r fig-gam-y, eval=T, fig.height=2.5, fig.width=6.5,out.width="1.0\\textwidth", fig.pos="H", fig.cap = "半参数回归模型非参数曲线", dev=c("cairo_pdf"),dev.args=list(family="Microsoft YaHei UI Light")}
par(mfrow = c(1,3))
par(mar=c(5,4,2,1))
plot.gam(gam.y,
         select=1,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="AQI",xlab = "废气治理投资"
         )
par(mar=c(5,3,2,1))
plot.gam(gam.y,
         select=2,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "汽车拥有量"
         )
par(mar=c(5,3,2,1))
plot.gam(gam.y,
         select=3,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "平均气温"
         )

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "coast", "heating", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
gamm.y <- gamm(AQI~te(invest)+te(car)+gas_control+te(mean_temp)+rain+humid+wind_speed+pressure+coast+heating+lat,
               random=list(city=~1), data=dat.sel.y, method = "REML")

@@

```{r fig-gamm-y, eval=T, fig.height=2.5, fig.width=6.5,out.width="1.0\\textwidth", fig.pos="H", fig.cap = "可加混合模型非参数曲线", dev=c("cairo_pdf"),dev.args=list(family="Microsoft YaHei UI Light")}
par(mfrow = c(1,3))
par(mar=c(5,4,2,1))
plot.gam(gamm.y$gam,
         select=1,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="AQI",xlab = "废气治理投资"
         )
par(mar=c(5,3,2,1))
plot.gam(gamm.y$gam,
         select=2,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "汽车拥有量"
         )
par(mar=c(5,3,2,1))
plot.gam(gamm.y$gam,
         select=3,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "平均气温"
         )

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "coast", "heating", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
gam.y.best <- gam(AQI~te(invest)+te(car)+gas_control+te(mean_temp)+wind_speed+coast+heating+lat,
                  data=dat.sel.y, method = "REML")

>>>>

library(gamsel)
gam1 <- gamsel(as.matrix(dat.sel.y[,-c(1:3, 23:24)]), as.matrix(dat.sel.y[,3]), gamma = 0.4)
## summary(gam1)

@@

library(gamsel)
gam1 <- gamsel(as.matrix(dat.sel.m[,-c(1:4, 24:25)]), as.matrix(log(dat.sel.m[,4])), gamma = 0.4)

par(mfrow=c(6,4), mar=c(2.1, 3.1, 2.1, 1.1))
## plot(gam1,newx=as.matrix(dat.sel.m[,-c(1, 23:24)]), index=22)
mapply(function(i, y) {
    plot(gam1,newx=as.matrix(dat.sel.m[,-c(1:4, 24:25)]),
         index=22, which = i, main = y, cex.main = 0.95, ylim = c(-0.2, 0.2))},
    as.list(1:22),
    as.list(varinfo[,2][-c(1:4, 19:20)]))

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "heating", "coast", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "heating", "coast", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
lme.y <- gamm(AQI~invest+car+gas_control+mean_temp+rain+humid+wind_speed+pressure+heating+coast+lat,
              random=list(city=~1), data=dat.sel.y, method = "REML")

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "heating", "coast", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
gam.y <- gam(AQI~te(invest)+te(car)+gas_control+te(mean_temp)+rain+humid+wind_speed+pressure+heating+coast+lat,
             data=dat.sel.y, method = "REML")

@@

```{r fig-gam-y, eval=T, fig.height=2.5, fig.width=6.5,out.width="1.0\\textwidth", fig.pos="H", fig.cap = "半参数回归模型非参数曲线", dev=c("cairo_pdf"),dev.args=list(family="Microsoft YaHei UI Light")}
par(mfrow = c(1,3))
par(mar=c(5,4,2,1))
plot.gam(gam.y,
         select=1,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="AQI",xlab = "固定资产投资额"
         )
par(mar=c(5,3,2,1))
plot.gam(gam.y,
         select=2,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "汽车拥有量"
         )
par(mar=c(5,3,2,1))
plot.gam(gam.y,
         select=3,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "平均气温"
         )

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "heating", "coast", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
gamm.y <- gamm(AQI~te(invest)+te(car)+gas_control+te(mean_temp)+rain+humid+wind_speed+pressure+heating+coast+lat,
               random=list(city=~1), data=dat.sel.y, method = "REML")

@@

```{r fig-gamm-y, eval=T, fig.height=2.5, fig.width=6.5,out.width="1.0\\textwidth", fig.pos="H", fig.cap = "可加混合模型非参数曲线", dev=c("cairo_pdf"),dev.args=list(family="Microsoft YaHei UI Light")}
par(mfrow = c(1,3))
par(mar=c(5,4,2,1))
plot.gam(gamm.y$gam,
         select=1,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="AQI",xlab = "固定资产投资额"
         )
par(mar=c(5,3,2,1))
plot.gam(gamm.y$gam,
         select=2,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "汽车拥有量"
         )
par(mar=c(5,3,2,1))
plot.gam(gamm.y$gam,
         select=3,
         col="blue",
         shade=T,
         shade.col="grey",
         ylab="",xlab = "平均气温"
         )

@@

varsel <- c("invest", "car", "gas_control", "mean_temp", "rain", "humid", "wind_speed", "pressure", "heating", "coast", "lat")
varselname <- varlist[match(varsel, as.character(varlist$var_code)), c(1:3,7)]
varselname <- as.character(varselname[order(varselname$var_no), 2])

library(mgcv)
gam.y.best <- gam(AQI~te(invest)+te(car)+gas_control+te(mean_temp)+wind_speed+heating+coast+lat,
                  data=dat.sel.y, method = "REML")
